Mitigating Interest Flooding DDoS Attacks in Named Data Networking

### 2012-12-03 03-interest-flooding.tex
Initial reorganization
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@846 df1a90cd-247b-4364-bdaf-287a704eb499
More reorganization and adding Makefile
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@847 df1a90cd-247b-4364-bdaf-287a704eb499
Correcting algorithms. Far far far from perfect...
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@849 df1a90cd-247b-4364-bdaf-287a704eb499

\section { DDoS Attacks in NDN \label{ddos-ndn}}
Any DoS attack aims to exhaust system resources. In the context of NDN by term "system" we understand two things: 1) every individual NDN router 2) a distributed system consisting of some collection of NDN routers. In a first case, every major data structure (FIB, CS, PIT) is a potential surface for denial of service attack. In a second case, we consider: 1) bandwidth between NDN routers 2) caching capabilities of NDN routers 3) packet processing capabilities of NDN routers.

@@

An infrastructure consisting of NDN routers is vulnerable to the following types of attacks: 
\begin{enumerate}
\item Interest flooding. 
\item fkjgkfjgkfg
\end{enumerate} 
%\begin{figure}[htpb]
%  \centering
%  \includegraphics[scale=0.5]{figures/sim-emu-power.pdf}
%  \caption{Strength of Interest flooding attack}
%  \label{fig:simemupower}
%\end{figure}

>>>>

\section{Interest Flooding in NDN}
\label{sec:interest flooding}

% Points here:
% - Definition of the Interest flooding attack
% - What makes Interest attack effective
% - Assumptions about the network, attackers, attack traffic, and legitimate consumers
% - References about other attacks and explicitly stating that this work aims to build a baseline for general Interest Flooding mitigation problem, with other attack profiles and malicious gateways.

Any DoS attack aims to exhaust system resources. In the context of NDN by term "system" we understand two things: 1) every individual NDN router 2) a distributed system consisting of some collection of NDN routers. In a first case, every major data structure (FIB, CS, PIT) is a potential surface for denial of service attack. In a second case, we consider: 1) bandwidth between NDN routers 2) caching capabilities of NDN routers 3) packet processing capabilities of NDN routers.

@@

The primary goal behind any flooding denial of service attack is to overwhelm network, CPU, or memory resources on routers or the target host.

% An infrastructure consisting of NDN routers is vulnerable to the following types of attacks: 
% \begin{enumerate}
% \item Interest flooding. 
% \item fkjgkfjgkfg
% \end{enumerate}

%\begin{figure}[htpb]
%  \centering
%  \includegraphics[scale=0.5]{figures/sim-emu-power.pdf}
%  \caption{Strength of Interest flooding attack}
%  \label{fig:simemupower}
%\end{figure}

### 2012-12-03 04-design.tex
Initial reorganization
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@846 df1a90cd-247b-4364-bdaf-287a704eb499
Correcting algorithms. Far far far from perfect...
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@849 df1a90cd-247b-4364-bdaf-287a704eb499

\section{Design}
\label{sec:design}

\subsection{Interest satisfaction statistics}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=4.5cm]{trivial-topo}
  \caption{Trivial topology (all links are 3Mbps/10ms)}
  \label{fig:trivial topology}
\end{figure}

\begin{figure}[htbp]
  \centering
  \includegraphics[scale=1]{limits}
  \caption{Dynamics of the unsatisfied Interests statistics on gateway's interface towards the attacker}
  \label{fig:ratio example}
\end{figure}

>>>>

\section{Interest flooding mitigation methods}
\label{sec:design}

% Points what should be here:
% - What can be done (in general) to mitigate flooding attack
% - Which building blocks NDN architecture gives to mitigate Interest flooding attacks: Interest limits, ability to measure Interest satisfaction performance (Interest satisfaction stats)
% - Methods to set these limits: static/dynamic
% - Methods how limits can be applied: best-effort (fifo), "fair" queuing, probabilistic
% - Reference to caching: we don't consider it here, but caching provides additional level of protection, especially for certain types of attacks

% Our definition of attack mitigation is that good clients are still able to access data on the producer.

In this section we present several methods to mitigate Interest flooding attacks in NDN, featuring different degrees of implementation complexity, as well as different degrees of effectiveness.

The presented methods rely on the core NDN principle of the flow balance between Interest and Data packets: Data packet can be forwarded only in response to the incoming Interest and each Interest is satisfied by at most one Data packet.
As a result of this principle, all traffic on NDN is ``receiver''-driven, where the ``receiver'' is either a user or any router on the path between the user and a Data producer.
Therefore, any node can limit the number of forwarded Interests, effectively limiting the amount of the retrieved Data.
At the same time, each forwarded Interest can be used to build up various data plane performance statistics, such as per-incoming interface ratios of satisfied Interests.

% Combining per-incoming interface data plane performance statistics with

% Disclaimer
% The presented solutions to mitigate Interest flooding DDoS attacks

% In particular, we explore different mechanisms to app

% Basic limits, probablity based on statistics, and dynamic window adjustment

\input{algos/physical-limits.tex}

\input{algos/stats.tex}

\input{algos/fair-queueing.tex}

\input{algos/probabilistic.tex}

\input{algos/dynamic-limits.tex}

### 2012-12-03 algos/fair-queueing.tex
Correcting algorithms. Far far far from perfect...
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@849 df1a90cd-247b-4364-bdaf-287a704eb499

Physical limits (per-outgoing-interface) described in Section~\ref{sec:physical limits} provide ability to fully utilize a downstream link, (almost completely) avoiding congestion in the link.
However, this limitation approach does not attempt to utilize data plane performance knowledge (i.e., Interest satisfaction ratio statistics) to discriminate good and malicious Interests.

@@

\begin{algorithm}[h]
\caption{Physical limits with ``fair'' queueing}
\label{alg:queuing}
\begin{algorithmic}[1]
\Function{InInterest}{Interest $i$, InFace $if$}
\For{\textbf{each} OutFace $of$ \textbf{in} ForwardingDecision($i,if$)}
    \If{$of$ is under physical limits}
        \State Forward($i$, $of$)
    \Else
        \State Queue $q \leftarrow of$.GetQueueByClass($if$)
        \State $q$.PushInterest($i$)
        \State $q$.UpdateWeight($if$.GetSatisfactionRatio())
    \EndIf
\EndFor
\EndFunction

\vspace{0.2cm}
\State{} \Comment{\textit{Called when an Interest is satisfied or times out}}
\Function{OnReady}{OutFace $of$}
    \State{} \Comment{\textit{get a non-empty queue using weighted round-robin}}
    \State Queue $q \leftarrow$ $of$.GetNonEmptyQueue 
    \State $i \leftarrow$ $q$.PopInterest
    \State Forward($i$, $of$)
\EndFunction
\end{algorithmic}
\end{algorithm}

>>>>

Physical limits (per-outgoing-interface) described in Section~\ref{sec:physical limits} provide ability to fully utilize a downstream link, largely avoiding congestion in the link.
However, this limitation approach does not attempt to utilize data plane performance knowledge (i.e., Interest satisfaction ratio statistics) to discriminate good and malicious Interests.

@@

\begin{algorithm}[h]
\caption{Physical limits with ``fair'' queueing}
\label{alg:queuing}
\begin{algorithmic}[1]
\Function{InInterest}{Interest $i$, InInterface $if$}
\For{\textbf{each} OutInterface $of$ \textbf{in} FwDecision($i,if$)}
    \If{$of$ is under physical limits}
        \State Forward($i$, $of$)
    \Else
        \State Queue $q \leftarrow of$.GetQueueByClass($if$)
        \State $q$.PushInterest($i$)
    \EndIf
\EndFor
\EndFunction

\vspace{0.2cm}
\State{} \Comment{\textit{Called when an Interest is satisfied or times out}}
\Function{OnReady}{OutInterface $of$}
    \State{} \Comment{\textit{get a non-empty queue using round-robin}}
    \State Queue $q \leftarrow$ $of$.GetNonEmptyQueue 
    \State $i \leftarrow$ $q$.PopInterest
    \State Forward($i$, $of$)
\EndFunction
\end{algorithmic}
\end{algorithm}
